---
title: "Main Functions"
format: html
---

```{r}
library(plasticair)
plastic_data <- load_data()
```


```{r}
plot_air_vs_plastic(air_vs_plastic_clean, 
                    remove_outliers = TRUE, 
                    aqi_filter = "All",
                    color = TRUE)
```

This function will create a bubble plot comparing total plastic waste and average AQI across countries. Users can filter countries by AQI category, remove outliers, and color points by AQI classification.

```{r}
summarize_country_pollution(
  air_vs_plastic_clean,
  country = "Philippines"
)
```
This function will summarize total plastic waste, AQI, and volunteer participation for a selected country with the default set as the Philippines and display it in a table format.

```{r}
animate_feritile_country(
  fertility,
  country =  "Philippines",
  replacement_rate = 2.1
)
```

This function will animate fertility rate over time for the Philippines. The x-axis will show year, the y-axis will show fertility rate, and the dashed line will represent the replacement rate of 2.1 births per woman.
